Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-03-21 ProbabilisticCoherence.tex
Updated section 5

\documentclass[a4paper, 11pt]{article}
\usepackage{monashwp}
\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx, mathrsfs, float, booktabs}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
\DeclareNameAlias{sortname}{last-first}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
\def\mathbi#1{\textit{ #1}}
\def\mathB#1{\textbf{ #1}}
\def\E{\text{E}}
\mathtoolsset{showonlyrefs=true}

@@

Although there is a rich and growing literature on producing coherent point forecasts of hierarchical time series, little  attention has been given to coherent probabilistic forecasts. The only relevant paper we are aware of is \citet{BenTaieb2017}, who recently proposed an algorithm to produce coherent probabilistic forecasts and applied it to UK electricity smart meter data. In their approach, a sample from the bottom level predictive distribution is first generated, and then aggregated to obtain coherent probabilistic forecasts of the upper levels of the hierarchy. Hence this method is a bottom-up approach. They propose to first use the MinT algorithm to reconcile the means of the bottom level forecast distributions, and then a copula-based approach is employed to model the dependency structure of the hierarchy. The resulting multi-dimensional distribution is used to generating empirical forecast distributions for all bottom-level series. Thus, while \citet{BenTaieb2017} provide coherent probabilistic forecasts, they do no forecast reconciliation of the distributions. In that sense, their approach is analogous to bottom-up point forecasting rather than forecast reconciliation.

@@

\begin{definition}[Coherent subspace]
Suppose an $n$-dimensional time series $\bm{y}_t \in \mathbb{R}^n$ is subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$ where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix. Let $\mathbb{C}^m$ be an $m$-dimensional subspace of $\mathbb{R}^n$, where $\mathbb{C}^m < \mathbb{R}^n$. Then $\mathbb{C}^m$ is said to be a coherent space if it is spanned by the columns of $\bm{S}$. 
\end{definition}

@@

\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
  Let $(\mathbb{R}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability triple where $\mathscr{F}^m$ is a $\sigma$-algebra on $\mathbb{R}^m$. Then, $(\mathbb{C}, \mathscr{F}_{\bm{S}}, \breve{\nu})$ is said to be a coherent probability measure space iff
  $$
      \breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall  \bm{A} \in \mathscr{F}^m,
    $$ 
  where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$. 
\end{definition}

@@

\citet{Hyndman2011} proposed to choose
\begin{equation*}
\tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h},
\end{equation*}
where in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy are given by,
\begin{equation}
\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}.
\end{equation}
They referred this to as the OLS solution and the loss function they considered is equivalent to the Euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$; i.e. $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>$.

@@

Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$ where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$. Then from \eqref{4.7} it follows that
\begin{equation}
\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
\end{equation}
Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is\\
$\mathscr{N}(\bm{SP}\bm{\hat{\mu}}_{t+h},~ \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}')$.

@@

The necessary final step in hierarchical forecasting is to make sure that our forecast distributions are accurate enough to predict the uncertain future. In general, forecasters prefer to maximize the sharpness of the predictive distribution subject to the calibration \citep{Gneiting2014}. Therefore the probabilistic forecasts should be evaluated with respect to these two properties.

Calibration refers to the statistical compatibility between probabilistic forecasts and realizations. In other words, random draws from a perfectly calibrated predictive distribution should be equivalent to the realizations. On the other hand, sharpness refers to the spread or the concentration of prediction distributions and it is a property of forecasts only. The more concentrated the predictive distributions, the sharper the forecasts are \citep{Gneiting2008}. However, independently assessing the calibration and sharpness will not help to properly evaluate the probabilistic forecasts. Therefore to assess these properties simultaneously, we use scoring rules.

Scoring rules are summary measures obtained based on the relationship between predictive distribution and the realizations. In some studies, researchers take the scoring rules to be positively oriented which they would wish to maximize \citep{Gneiting2007}. However, scoring rules were also defined to be negatively oriented which forecasters wish to minimize \citep{Gneiting2014}. We consider these negatively oriented scoring rules to evaluate probabilistic forecasts in hierarchical time series.

Let $\breve{\bm{Y}}$ and $\bm{Y}$ be a $n$-dimensional random vectors from the predictive distribution $\bm{F}$ and the true distribution $\bm{G}$. Further let $\bm{y}$ be a $n$-dimensional realization. Then the scoring rule is a numerical value $S(\breve{\bm{Y}},\bm{y})$ assign to each pair $(\breve{\bm{Y}},\bm{y})$ and the proper scoring rule is defined as,
\begin{equation}\label{eq:(3.1.)}
\E_{\bm{G}}[S(\bm{Y},\bm{y})] \le \E_{\bm{G}}[S(\breve{\bm{Y}},\bm{y})],
\end{equation}
where $\E_{\bm{G}}[S(\bm{Y,y})]$ is the expected score under the true distribution $\bm{G}$ \citep{Gneiting2008, Gneiting2014}.

Table \ref{table:scoringrules} summarizes few existing proper scoring rules.

\begin{table}[!b]
  \caption{Scoring rules to evaluate multivariate forecast densities. $\breve{\bm{y}}_{T+h}$ and $\breve{\bm{y}}^*_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(\cdot)$ at time $T+h$ and $\bm{y}_{T+h}$ is the vector of realizations. Further $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are $i$th and $j$th components of the vector $\breve{\bm{Y}}_{T+h}$. Further the variogram score is given for order $p$ where, $w_{ij}$ are non-negative weights.}\label{table:scoringrules}
  \centering\small\setstretch{1.3}
  \begin{tabular}{@{}lp{8.1cm}l@{}}
    \toprule
    \textbf{Scoring rule}  & \textbf{Expression} & \textbf{Reference}           \\
    \midrule
    \text{Log score}       &
    $\text{LS}(\breve{\bm{F}},\bm{y}_{T+h}) = -\log {\breve{\bm{f}}(\bm{y}_{T+h})}$ &
    \citet{Gneiting2007}  \\\\[-0.2cm]
    \text{Energy score}    &
    $\text{eS}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) =
    \E_{\breve{\bm{F}}}
    \|\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}\|^\alpha -$ \par\hfill
    $\frac{1}{2}\E_{\breve{\bm{F}}}\|\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}^*_{T+h}\|^\alpha$, \,\, $\alpha \in (0,2]$ &
    \citet{Gneiting2008}  \\\\[-0.2cm]
    \text{Variogram score} &
    $\text{VS}(\breve{\bm{F}}, \bm{y}_{T+h}) =
    \sum\limits_{i=1}^{n}
    \sum\limits_{j=1}^{n}
    w_{ij}\Big(|y_{T+h,i} - y_{T+h,j}|^p -$ \par\hfill
    $\E_{\breve{\bm{F}}}|\breve{Y}_{T+h,i}-\breve{Y}_{T+h,j}|^p\Big)^2$     &
    \citet{SCHEUERER2015} \\
    \bottomrule
  \end{tabular}
\end{table}

Even though the log score can be used evaluate simulated forecast densities with large samples \citep{Jordan2017}, it is more convenient to use if it is reasonable to assume a parametric forecast density for the hierarchy. However, the \qq{degenerecy} of coherent forecast densities would be problematic when using log scores. We will discuss more on this in the next subsection.

In the energy score, for $\alpha=2$, it can be easily shown that
\begin{equation} \label{eq:(5.1)}
\text{eS}(\breve{\bm{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
\end{equation}
where $\breve{\bm{\mu}}_{T+h} =\E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $. Therefore in the limiting case, the energy score only measures the accuracy of the forecast mean, but not the entire distribution. Further \citet{Pinson2013a} argued that the Energy score given in Table \ref{table:scoringrules} has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well.

However, \citet{SCHEUERER2015} have shown that the variogram score has a high discrimination ability of misspecified means, variance and correlation structure than the Energy score. Further they suggested the variogram score with $p=0.5$ is more powerful.

For a possible finite sample of size $B$ from the multivariate forecast density $\breve{\bm{F}}$, the variogram score is defined as,
\begin{equation}
\text{VS}(\breve{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - \frac{1}{B} \displaystyle\sum_{k=1}^{B} |\breve{Y}^k_{T+h,i}-\breve{Y}^k_{T+h,j}|^p\right)^2.
\end{equation}

@@

As it was mentioned in the previous section, any coherent hierarchical forecast density is a degenerate density. To the best of our knowledge, there is no proper multivariate scoring rule in literature to evaluate degenerate densities. Further it can be easily seen that some of the existing scoring rules breakdown under the degeneracy. For example take the log score in the univariate case. Suppose the true density is degenerate at $x=0$, i.e. $f(x)=\mathbb{1}\{x=0\}$.  Now consider two predictive densities $p_1(x)$ and $p_2(x)$. Let $p_1(x)$ is equivalent to the true density, i.e. $p_1(x)=\mathbb{1}\{x=0\}$ and $p_2(x) =^d N(0,\sigma^2)$ with $\sigma^2 < (2\pi)^{-1}$. The expected log score of $p_1$ is:
$$
\E_f[S(f,f)] = \E_f[S(p_1,f)] = -\log[p_1(x=0)]=0,
$$
and that of $p_2$ is:
$$
\E_f[S(p_2,f)] = -\log[p_2(x=0)]<0.
$$
Therefore $S(f,f) > S(p_2,f)$ and hence there exist at least one forecast density which breaks the condition \eqref{eq:(3.1.)} for proper scoring rule. This implies log score cannot be used to evaluate the degenerate densities.

Thus it is necessary to have a rule of thumb to use these scoring rules in order to evaluate coherent forecast densities. First we should notice that, even though the coherent distribution of the entire hierarchy is degenerate, the density of the basis set of series is non-degenerate since these series are linearly independent. Further, if we can correctly specify the forecast distribution of these basis set of series, then we have almost obtained the correct forecast distribution of the whole hierarchy. Therefore, we propose to evaluate the predictive ability of only the basis set of series of the coherent forecast density by using any of the above discussed multivariate scoring rules. This will also avoid the impact of degeneracy for the scoring rules.

For example, since the bottom level series is a set of basis series for a given hierarchy, we can evaluate the predictive ability of the bottom level series of the coherent forecast distribution instead of evaluating the whole distribution. Further, if our purpose is to compare two coherent forecast densities, we can compare the forecast ability of only the bottom level forecast densities.

@@

It is also important to assess how the coherent or reconciled forecast densities improve the predictive ability compared to the incoherent forecasts. Clearly, we cannot use multivariate scoring rules, even for the basis set of series, since the coherent and incoherent forecast densities lie in two different matrix spaces.

However we could compare individual margins of the forecast density of the hierarchy using univariate proper scoring rules. Most widely used Continuous Ranked Probability Score (CRPS) would be helpful for this.
\begin{equation} \label{eq:(3.6)}
\text{CRPS}(\breve{F}_i,y_{T+h,i}) = \E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}\E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|,
\end{equation}
where $\breve{Y}_{T+h,i}$ and $\breve{Y}^*_{T+h,i}$ are two independent copies from the $i$th reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i$th realization from the true marginal distribution $G_i$. We can also use univariate log scores for which we could assume a parametric forecast distribution.

@@

Main purpose of this section is to establish the importance of reconciliation in probabilistic hierarchical forecasting. We narrow down the simulation setting for the Gaussian framework in this work. That is, suppose all the historical data in the hierarchy follows a multivariate Gaussian distribution, i.e. $\bm{y}_T \sim \mathscr{N}(\bm{\mu}_T, \bm{\Sigma}_T)$ where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ lives in $\mathbb{C}^m$ by nature of the hierarchical time series. We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$ where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,\dots.,\bm{y}_T\}$, which should also lives in $\mathbb{C}^m$.

@@

From \eqref{eq:(6.02)} it immediately follows that,
\begin{align*}
&\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] \overset{p}{\to} \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T],
\end{align*}
\begin{equation}
\bm{W}_{T+h} \overset{p}{\to} \text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) \quad \text{as} \quad T \to \infty,
\end{equation}
where, $\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = \bm{W}_{T+h}$.

@@

Since our primary objective is to find the coherent forecast density of the hierarchy, we need to reconciled \eqref{eq:(6.03)}. Recalling from example 2, the reconciled Gaussian predictive distribution is then given by,
\begin{equation}\label{eq:(6.04)}
\widetilde{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathscr{N}(\bm{SP}\hat{\bm{Y}}_{T+h}, \bm{SP}\bm{W}_{T+h}\bm{P}'\bm{S}')
\end{equation}
where, $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.

@@

Suppose $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from $ARIMA(p,d,q)$ processes where, $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability. Further, the contemporaneous errors $\{\epsilon_{AA,t},\epsilon_{AB,t},\epsilon_{BA,t},\epsilon_{BB,t}\} \sim \mathcal{N}(\bm{0}, \bm{\Sigma})$. The parameters for $AR$ and $MA$ components will be randomly and uniformly generated from $[0.3,0.5]$ and $[0.3,0.7]$ respectively. Then the bottom level series $\{y_{AA,t},y_{AB,t},y_{BA,t},y_{BB,t}\}$ will be obtained as:
\begin{align*}
y_{AA,t} &= w_{AA,t} + u_t - 0.5v_t,\\
y_{AB,t} &= w_{AB,t} - u_t - 0.5v_t,\\
y_{BA,t} &= w_{BA,t} + u_t + 0.5v_t,\\
y_{BB,t} &= w_{BB,t} - u_t + 0.5v_t,
\end{align*}
where $u_t \sim N(0,\sigma^2_u)$ and $v_t \sim N(0,\sigma^2_v)$.

>>>>

\documentclass[a4paper, 11pt]{article}
\usepackage{monashwp}
\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx}
\usepackage{mathrsfs, float, booktabs,todonotes}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
\DeclareNameAlias{sortname}{last-first}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
\def\mathbi#1{\textit{ #1}}
\def\mathB#1{\textbf{ #1}}
\def\E{\text{E}}
\mathtoolsset{showonlyrefs=true}

@@

Although there is a rich and growing literature on producing coherent point forecasts of hierarchical time series, little  attention has been given to coherent probabilistic forecasts. The only relevant paper we are aware of is \citet{BenTaieb2017}, who recently proposed an algorithm to produce coherent probabilistic forecasts and applied it to UK electricity smart meter data. In their approach, a sample from the bottom level forecast distribution is first generated, and then aggregated to obtain coherent probabilistic forecasts of the upper levels of the hierarchy. Hence this method is a bottom-up approach. They propose to first use the MinT algorithm to reconcile the means of the bottom level forecast distributions, and then a copula-based approach is employed to model the dependency structure of the hierarchy. The resulting multi-dimensional distribution is used to generating empirical forecast distributions for all bottom-level series. Thus, while \citet{BenTaieb2017} provide coherent probabilistic forecasts, they do no forecast reconciliation of the distributions. In that sense, their approach is analogous to bottom-up point forecasting rather than forecast reconciliation.

@@

\begin{definition}[Coherent subspace]
Suppose an $n$-dimensional time series $\bm{y}_t \in \mathbb{R}^n$ is subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$, where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix. Let $\mathbb{C}^m$ be an $m$-dimensional subspace of $\mathbb{R}^n$, where $\mathbb{C}^m < \mathbb{R}^n$. Then $\mathbb{C}^m$ is said to be a coherent space if it is spanned by the columns of $\bm{S}$. 
\end{definition}

@@

\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
  Let $(\mathbb{R}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability triple, where $\mathscr{F}^m$ is a $\sigma$-algebra on $\mathbb{R}^m$. Then, $(\mathbb{C}, \mathscr{F}_{\bm{S}}, \breve{\nu})$ is said to be a coherent probability measure space iff
  $$
      \breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall  \bm{A} \in \mathscr{F}^m,
    $$ 
  where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$. 
\end{definition}

@@

\citet{Hyndman2011} proposed to choose
\begin{equation*}
\tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h},
\end{equation*}
where, in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy are given by,
\begin{equation}
\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}.
\end{equation}
They referred this to as the OLS solution and the loss function they considered is equivalent to the Euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$; i.e. $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>$.

@@

Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$. Then from \eqref{4.7} it follows that
\begin{equation}
\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
\end{equation}
Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is\\
$\mathscr{N}(\bm{SP}\bm{\hat{\mu}}_{t+h},~ \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}')$.

@@

The necessary final step in hierarchical forecasting is to make sure that our forecast distributions are accurately predicting the uncertain future. In general, forecasters prefer to maximize the sharpness of the forecast distribution subject to the calibration \citep{Gneiting2014}. Therefore the probabilistic forecasts should be evaluated with respect to these two properties.

Calibration refers to the statistical compatibility between probabilistic forecasts and realizations. In other words, random draws from a perfectly calibrated forecast distribution should be equivalent in distribution to the realizations. On the other hand, sharpness refers to the spread or the concentration of the prediction distributions and it is a property of the forecasts only. The more concentrated the forecast distributions, the sharper the forecasts \citep{Gneiting2008}. However, independently assessing the calibration and sharpness will not help to properly evaluate the probabilistic forecasts. Therefore we need to assess these properties simultaneously using scoring rules.

Scoring rules are summary measures obtained based on the relationship between the forecast distributions and the realizations. In some studies, researchers take the scoring rules to be positively oriented, in which case the scores should be maximized \citep{Gneiting2007}. However, scoring rules have also been defined to be negatively oriented, and then the scores should be minimized \citep{Gneiting2014}. We consider negatively oriented scoring rules to evaluate probabilistic forecasts in hierarchical time series.

Let $\breve{\bm{Y}}$ and $\bm{Y}$ be $n$-dimensional random vectors from the forecast distribution $\bm{F}$ and the true distribution $\bm{G}$, respectively. Further let $\bm{y}$ be an $n$-dimensional realization from $\bm{G}$. Then a scoring rule is a numerical value $S(\breve{\bm{Y}},\bm{y})$ assigned to each pair $(\breve{\bm{Y}},\bm{y})$. It is a ``proper'' scoring rule if 
\begin{equation}\label{eq:(3.1.)}
\E_{\bm{G}}[S(\bm{Y},\bm{y})] \le \E_{\bm{G}}[S(\breve{\bm{Y}},\bm{y})],
\end{equation}
where $\E_{\bm{G}}[S(\bm{Y,y})]$ is the expected score under the true distribution $\bm{G}$ \citep{Gneiting2008, Gneiting2014}.

Table \ref{table:scoringrules} summarizes a few existing proper scoring rules.

\begin{table}[!bh]
  \caption{Scoring rules to evaluate multivariate forecast densities. Here, $\breve{\bm{y}}_{T+h}$ and $\breve{\bm{y}}^*_{T+h}$ are two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with density function $\breve{\bm{f}}(\cdot)$ at time $T+h$, and $\bm{y}_{T+h}$ is the vector of realizations. Further, $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are the $i$th and $j$th components of the vector $\breve{\bm{Y}}_{T+h}$. The variogram score is given for order $p$, where $w_{ij}$ denote non-negative weights.}\label{table:scoringrules}
  \centering\small\setstretch{1.3}
  \begin{tabular}{@{}lp{8.1cm}l@{}}
    \toprule
    \textbf{Scoring rule}  & \textbf{Expression} & \textbf{Reference}           \\
    \midrule
    \text{Log score}       &
    $\text{LS}(\breve{\bm{F}},\bm{y}_{T+h}) = -\log {\breve{\bm{f}}(\bm{y}_{T+h})}$ &
    \citet{Gneiting2007}  \\\\[-0.2cm]
    \text{Energy score}    &
    $\text{eS}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) =
    \E_{\breve{\bm{F}}}
    \|\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}\|^\alpha -$ \par\hfill
    $\frac{1}{2}\E_{\breve{\bm{F}}}\|\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}^*_{T+h}\|^\alpha$, \,\, $\alpha \in (0,2]$ &
    \citet{Gneiting2008}  \\\\[-0.2cm]
    \text{Variogram score} &
    $\text{VS}(\breve{\bm{F}}, \bm{y}_{T+h}) =
    \sum\limits_{i=1}^{n}
    \sum\limits_{j=1}^{n}
    w_{ij}\Big(|y_{T+h,i} - y_{T+h,j}|^p -$ \par\hfill
    $\E_{\breve{\bm{F}}}|\breve{Y}_{T+h,i}-\breve{Y}_{T+h,j}|^p\Big)^2$     &
    \citet{SCHEUERER2015} \\
    \bottomrule
  \end{tabular}
\end{table}

Even though the log score can be used to evaluate simulated forecast densities with large samples \citep{Jordan2017}, it is more convenient to use if we can assume a parametric forecast density for the hierarchy. However, the degeneracy of coherent forecast densities is problematic when using log scores. We will discuss this further in the next subsection.

For the energy score with $\alpha=2$, it can be easily shown that
\begin{equation} \label{eq:(5.1)}
\text{eS}(\breve{\bm{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
\end{equation}
where $\breve{\bm{\mu}}_{T+h} =\E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $. Therefore, in the limiting case, the energy score only measures the accuracy of the forecast mean, and not the entire distribution. Similarly, \citet{Pinson2013a} argued that the energy score given in Table \ref{table:scoringrules} has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well.

In contrast, \citet{SCHEUERER2015} have shown that the variogram score has a higher discrimination ability of misspecified means, variances and correlation structures than the energy score. For a finite sample of size $B$ from the multivariate forecast density $\breve{\bm{F}}$, the empirical variogram score is defined as
\begin{equation}
\text{VS}(\breve{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - \frac{1}{B} \displaystyle\sum_{k=1}^{B} |\breve{Y}^k_{T+h,i}-\breve{Y}^k_{T+h,j}|^p\right)^2.
\end{equation}
\citet{SCHEUERER2015} recommend using $p=0.5$.

@@

Any coherent hierarchical forecast density is a degenerate density. To the best of our knowledge, there is no proper multivariate scoring rule available to evaluate degenerate densities. Further, it can easily be seen that some of the existing scoring rules breakdown under degeneracy.

For example, consider the log score in the univariate case. Suppose the true density is degenerate at $x=0$, i.e. $f(x)=\mathbb{1}\{x=0\}$. \todo{I think you need Dirac delta functions here.}  Now consider two predictive densities $p_1(x)$ and $p_2(x)$. Let $p_1(x)$ be equivalent to the true density, i.e. $p_1(x)=\mathbb{1}\{x=0\}$, and let $p_2(x) \sim N(0,\sigma^2)$ with $\sigma^2 < (2\pi)^{-1}$. The expected log score of $p_1$ is
$$
\E_f[S(f,f)] = \E_f[S(p_1,f)] = -\log[p_1(x=0)]=0,
$$
while that of $p_2$ is
$$
\E_f[S(p_2,f)] = -\log[p_2(x=0)]<0.
$$
Therefore $S(f,f) > S(p_2,f)$, and there exists at least one forecast density which breaks the condition \eqref{eq:(3.1.)} for a proper scoring rule. This implies that the log score cannot be used to evaluate the degenerate densities.

However, even though the coherent distribution of the entire hierarchy is degenerate, the density of the basis set of series is non-degenerate since these series are linearly independent. Further, if we can correctly specify the forecast distribution of the basis set of series, then we have almost obtained the correct forecast distribution of the whole hierarchy. Therefore, we propose to evaluate the forecast distributions using only the basis set of series. Then we can use any of the multivariate scoring rules discussed above without incurring problems due to degeneracy.

For example, since the bottom level series forms a set of basis series for a given hierarchy, we can evaluate the coherent forecast distribution using only the bottom level series instead of evaluating the whole distribution. In particular, if our purpose is to compare two coherent forecast densities, we can compare them using only the bottom level forecast densities.

@@

It is also important to assess how the coherent or reconciled forecast densities improve the predictive ability compared to the incoherent forecasts. Clearly, we cannot use multivariate scoring rules, even for the basis set of series, since the coherent and incoherent forecast densities lie in two different metric spaces.

However we could compare the individual margins of the forecast density of the hierarchy using univariate proper scoring rules. The widely used Continuous Ranked Probability Score (CRPS) could then be used. This is defined as
\begin{equation} \label{eq:(3.6)}
\text{CRPS}(\breve{F}_i,y_{T+h,i}) = \E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}\E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|,
\end{equation}
where $\breve{Y}_{T+h,i}$ and $\breve{Y}^*_{T+h,i}$ are two independent copies from the $i$th reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy, and $y_{T+h,i}$ is the $i$th realization from the true marginal distribution $G_i$. We could also use univariate log scores, for which we could assume a parametric forecast distribution.

@@

Main purpose of this section is to establish the importance of reconciliation in probabilistic hierarchical forecasting. We narrow down the simulation setting for the Gaussian framework in this work. That is, suppose all the historical data in the hierarchy follows a multivariate Gaussian distribution, i.e. $\bm{y}_T \sim \mathscr{N}(\bm{\mu}_T, \bm{\Sigma}_T)$, where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ lives in $\mathbb{C}^m$ by nature of the hierarchical time series. We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$, where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,\dots.,\bm{y}_T\}$, which should also live in $\mathbb{C}^m$.

@@

From \eqref{eq:(6.02)} it immediately follows that,
\begin{align*}
&\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] \overset{p}{\to} \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T],
\end{align*}
\begin{equation}
\bm{W}_{T+h} \overset{p}{\to} \text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) \quad \text{as} \quad T \to \infty,
\end{equation}
where $\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = \bm{W}_{T+h}$.

@@

Since our primary objective is to find the coherent forecast density of the hierarchy, we need to reconciled \eqref{eq:(6.03)}. Recalling from example 2, the reconciled Gaussian forecast distribution is then given by,
\begin{equation}\label{eq:(6.04)}
\widetilde{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathscr{N}(\bm{SP}\hat{\bm{Y}}_{T+h}, \bm{SP}\bm{W}_{T+h}\bm{P}'\bm{S}'),
\end{equation}
where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.

@@

Suppose $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from $ARIMA(p,d,q)$ processes, where $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability. Further, the contemporaneous errors $\{\epsilon_{AA,t},\epsilon_{AB,t},\epsilon_{BA,t},\epsilon_{BB,t}\} \sim \mathcal{N}(\bm{0}, \bm{\Sigma})$. The parameters for $AR$ and $MA$ components will be randomly and uniformly generated from $[0.3,0.5]$ and $[0.3,0.7]$ respectively. Then the bottom level series $\{y_{AA,t},y_{AB,t},y_{BA,t},y_{BB,t}\}$ will be obtained as:
\begin{align*}
y_{AA,t} &= w_{AA,t} + u_t - 0.5v_t,\\
y_{AB,t} &= w_{AB,t} - u_t - 0.5v_t,\\
y_{BA,t} &= w_{BA,t} + u_t + 0.5v_t,\\
y_{BB,t} &= w_{BB,t} - u_t + 0.5v_t,
\end{align*}
where $u_t \sim N(0,\sigma^2_u)$ and $v_t \sim N(0,\sigma^2_v)$.
